Deterministic Scheduling of Periodic Messages for Cloud RAN

### 2017-07-24 infocom/infocom.tex

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
      \end{center}
            \vspace{-0.75cm}
      \caption{Minimum period averaged over $1000$ random instances}\label{fig:short}
      \end{figure}
      First, we remark that the exhaustive search finds a solution even when the load is high, especially when there are more routes.
      It justifies the idea to look for an assignment without waiting time, in this short routes regime.
      Second, remark that the Shortest-Longest algorithm is as good as the exhaustive search. While it was expected to be good with short routes, it turns out to be optimal for all the the random star routed networks we have tried. Therefore, we should use it in practical applications with short routes, instead of the exhaustive search which is much more computationally expensive. 
      Finally, note that the greedy algorithm works on average when the load is less than       which is twice better than the theoritical bound. This algorithm seems to depends on the load only and not on the number of routes (linear regression).

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate for $8$ routes over $1000$ random instances}\label{fig:long}
     \end{figure}

@@

  \centering
     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
\vspace{-0.75cm}
      \caption{Success rate of different orders, $95\%$ load.}
      \label{fig:success95}
          \end{figure}
          \vspace{-1cm}
\begin{figure}[h] 
          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
          \vspace{-0.5cm}
      \caption{Success rate of different orders, $80\%$ load.}
           \label{fig:success80}
     \end{figure}

@@

    \begin{figure} [h] 
      \vspace{-0.5cm}
       \begin{center}
      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate of GD, MLS and PMLS, $95\%$ load}
     \label{fig:success21000}
       \vspace{-0.2cm}
     \end{figure}
     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that \emph{taking into account the periodicity is fundamental}.
     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $97\%$ of the experiments, even with a margin $0$. Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution. However, with a margin of $1,000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.

    Recall that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order. The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate. Up to now, we chose $1,000$ random orders arbitrarily. We investigate the success rate of our algorithm with regards to the number of random orders drawn, a load of $95\%$ and a margin $0$. The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
         \begin{figure}[h] 
       \begin{center}
   \begin{tabularx}{0.5\textwidth}{|c|X|X|X|X|X|X|}
    \hline
    \# orders& $1$ & $10$ & $100$& $1,000$& $10^{4}$&$10^{5}$\\
    \hline
    GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
    \hline
  PMLS & $41.1$ &$82.5$&$94.5$&$96.2$&$97.2$&$97.2$\\
    \hline
      \end{tabularx}
      \end{center}
   \caption{Impact of the number of random sending orders}
     \end{figure}
First remark that we can improve our previous results by taking $10000$ random orders,
instead of $1000$. The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order. Therefore instead of doing $10000$ random draws we could test every possible order in less time. However the computation time of this method would scale badly with $n$. On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn becomes critical.

@@

       \begin{center}
     \hspace{-0.5cm} \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
       %\input{figures/stochastic}
      \end{center}
      \vspace{-1cm}
      \caption{First and third quartile of the margin of statistical multiplexing}
      \label{fig:sto}
     \end{figure}

>>>>

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.4\textwidth]{periode_petite.pdf}
      \end{center}
            \vspace{-0.75cm}
      \caption{Minimum period averaged over $1,000$ random instances}\label{fig:short}
      \end{figure}
      First, we remark that the exhaustive search finds a solution even when the load is high, especially when there are more routes.
      It justifies the idea to look for an assignment without waiting time, in this short routes regime.
      Second, remark that the Shortest-Longest algorithm is as good as the exhaustive search. While it was expected to be good with short routes, it turns out to be optimal for all the the random star routed networks we have tried. Therefore, we should use it in practical applications with short routes, instead of the exhaustive search which is much more computationally expensive. 
      Finally, note that the greedy algorithm works on average when the load is less than $2/3$ which is twice better than the theoretical bound. This algorithm seems to depends on the load only and not on the number of routes.

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.4\textwidth]{echec_longues.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate for $8$ routes over $1,000$ random instances}\label{fig:long}
     \end{figure}

@@

  \centering
     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
\vspace{-0.75cm}
      \caption{Success rate of different orders, $95\%$ load.}
      \label{fig:success95}
          \end{figure}
          \vspace{-1cm}
%\begin{figure}[h] 
%          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
%          \vspace{-0.5cm}
%      \caption{Success rate of different orders, $80\%$ load.}
%           \label{fig:success80}
%     \end{figure}

@@

    \begin{figure} [h] 
      \vspace{-0.5cm}
       \begin{center}
      \includegraphics[width=0.4\textwidth]{retour_21000.pdf}
      \end{center}
            \vspace{-1cm}

      \caption{Success rate of GD, MLS and PMLS, $95\%$ load}

     \label{fig:success21000}
       \vspace{-0.2cm}
     \end{figure}
     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that \emph{taking into account the periodicity is fundamental}.
     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $97\%$ of the experiments, even with a margin $0$. Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution. However, with a margin of $1,000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.

    Recall that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order. The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate. Up to now, we chose $1,000$ random orders arbitrarily. We investigate the success rate of our algorithm with regards to the number of random orders drawn, a load of $95\%$ and a margin $0$. The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
         \begin{figure}[h] 
       \begin{center}
   \begin{tabularx}{0.5\textwidth}{|c|X|X|X|X|X|X|}
    \hline
    \# orders& $1$ & $10$ & $100$& $1,000$& $10^{4}$&$10^{5}$\\
    \hline
    GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
    \hline
  PMLS & $41.1$ &$82.5$&$94.5$&$96.2$&$97.2$&$97.2$\\
    \hline
      \end{tabularx}
      \end{center}
   \caption{Impact of the number of random sending orders}
     \end{figure}

First remark that we can improve our previous results by taking $10000$ random orders,
instead of $1000$. The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order. Therefore instead of doing $10000$ random draws we could test every possible order in less time. However the computation time of this method would scale badly with $n$. On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn becomes critical.

@@

       \begin{center}
     \hspace{-0.5cm} \includegraphics[width = 0.4\textwidth]{stochastic.pdf}
       %\input{figures/stochastic}
      \end{center}
      \vspace{-1cm}
      \caption{First and third quartile of the margin of statistical multiplexing}
      \label{fig:sto}
     \end{figure}
